---
# install.packages("rmdformats") for formatting
title: "Prevelance of exclusionary nationalism across party manifestos, 1920-2021"
author: 
 - Sean Bock, Harvard University
 
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE
                      )
```

# Nationalism measures

The Comparative Manifesto Project (CMP) includes sets of content analytical variables. Each variable indicates the share of quasi-sentences in the respective category calculated as a fraction of the overall number of allocated codes per document. Below are selected measures related to exclusionary forms of nationalism. (See more on CMP [here](https://manifesto-project.wzb.eu/down/data/2020b/codebooks/codebook_MPDataset_MPDS2020b.pdf))

-   **National way of life: Positive**

    Favorable mentions of the manifesto country's nation, history, and general appeals. May include: Support for established national ideas; general appeals to pride of citizenship; appeals to patriotism; appeals to nationalism; suspension of some freedoms in order to protect the state against subversion.

-   **Immigration: Negative**

    Statement advocating the restriction of the process of immigration, i.e. accepting new immigrants. Might include statements regarding: Immigration being a threat to national character fo the manifesto country; \`the boat is full' argument; the introduction of migration quotas, including restricting immigration from specific countries or regions etc.

-   **Law and Order: Positive**

    Favorable mentions of strict law enforcement, and tougher actions against domestic crime. Only refers to the enforcement of the status quo of the manifesto country's law code. May include: Increasing support and resources for the police; tougher attitudes in courts; importance of internal security.

-   **Multiculturalism: Negative**

    The enforcement or encouragement of cultural integration. Appeals for cultural homogeneity in society

-   **Nationalism Index**

    To capture the overall level of exclusionary nationalism present in a given manifesto, we created an index, calculated as the sum of each nationalism variable. Items are normalized (i.e., between 0 and 1) before summing to weight each variable equally.

# Results

```{r get_data, include=FALSE, file="get_data.R"}
```

```{r cleaning_data, file="cleaning_data.R"}
```

<br>

```{r plot_interactive, fig.height=7, fig.width=10, file = "plot_interactive.R"}

```

<br>
<br>

```{r table, file= "table_top50.R", paged.print=TRUE}
```
